---
title: "Kavish_property_inferential"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
#options -----------------------------------
base::options(scipen=999,
              knitr.kable.NA = "-"
              )

knitr::opts_chunk$set(
	cache = FALSE,
  echo = TRUE,
	message = FALSE,
	warning = FALSE,
	error = FALSE,
	fig.retina = 3
)
```

## Configuration

List of the packages used and access to the data


```{r}
#libraries ----------------------------------------------------------
library(tidyverse)
library(psych)
library(here)
library(knitr)

#data ----------------------------------------------------------
daftdb <- here("data/daftdb.rds") %>%
  read_rds()
```

## New data frame created

The original dataframe is stored in another dataframe, "dfdb" for work purposes.

```{r}
(dfdb <- daftdb) %>%
  as_tibble()
```

## Filtering data
The rows are remove with houses either on auction or price not available. They were not replaced with 0's as this would skew the data.

```{r}
dfdb <- dfdb %>%
  filter(str_detect(price, "Reserve") == "FALSE") %>%
  filter(str_detect(price, "AMV") == "FALSE") %>%
  filter(str_detect(price, "Price") == "FALSE") %>% 
  print()
```

## Data Wrangling

The price column will be cleaned and converted into numeric type. Further, a new column is created specifying the Dublin areas of the properties**(Dublin 1,3,5,....)**.

```{r}
#replaced any string or commas --------------------------------------------------------
dfdb$price <- str_replace_all(dfdb$price, "[a-z,A-Z]","")

#euro sign removed-------------------------------------------------------------------
dfdb$price <- str_sub(dfdb$price,2)

#conversion time-------------------------------------------------------------------
dfdb$price=as.double(dfdb$price)
class(dfdb$price) #successful

#separating areas and adding "Co. Dublin" in place of NAs --------------------------
dfdb <- dfdb %>%
  mutate(dublin_code = str_extract(address, "Dublin [0-9]+")) %>%
  mutate(dublin_code = as.factor(dublin_code)) %>%
  mutate(dublin_code = fct_explicit_na(dublin_code, na_level = "Co. Dublin")) %>%
  print()
```


## Statistical analysis

Descriptive analysis and inferential analysis will be done in the following sections.

### Descriptive
Starting with correlation.

```{r}
#correlation between number of bathrooms and bedrooms vs price of the house -------------
cor.test(dfdb$bathroom, dfdb$price) #p-value < 0.05 : statistically significant
cor.test(dfdb$bedroom, dfdb$price) #p-value < 0.05 : statistically significant
```

The p-values in both the cases were found to be lesser than 0.05, hence there exist a correlation between the prices of properties and the number of bathrooms and bedrooms in the house.

Also, both the values show a positive correlation.

Further, a new table was created which stored difference in prices, number of bedrooms and bathrooms, and the original prices. It also contains 'r n_distinct(dfdb$address)' unique addresses and its respective Dublin area code.

```{r}
#calculating difference in prices --------------------------------------------------
diffdb <- dfdb %>%
  group_by(address, dublin_code) %>%
  summarise(price_diff = max(price) - min(price), bath=max(bathroom), 
            bed=max(bedroom), price=max(price)) %>%
  ungroup()
```


Several new columns will be added in order to conduct inferential analysis on the dataset in the table **diffdb**

```{r}
#creating new column to determine high and low-priced houses ---------------------
summary(diffdb$price)
diffdb$price_cat <- ifelse(diffdb$price > 400000,'High price','Low price') 
#another way of coding
#diffdb$price_cat <- ifelse(diffdb$price > 400000,1,0) #1=High, 0 = Low
diffdb <- diffdb %>%
  mutate(price_cat = as.factor(price_cat))

#creating new columns to determine higher and lower no. of bedrooms and bathrooms -----
summary(diffdb$bed)
diffdb$bed_cat <- ifelse(diffdb$bed > 3,'Higher bedrooms','Lower bedrooms')
diffdb <- diffdb %>%
  mutate(bed_cat = as.factor(bed_cat))

summary(diffdb$bath)
diffdb$bath_cat <- ifelse(diffdb$bath > 2,'Higher bathrooms','Lower bathrooms')
diffdb <- diffdb %>%
  mutate(bath_cat = as.factor(bath_cat))

#In real world, we ought to filter out houses with 0 bathrooms and 0 bedrooms
#Technically, this won't be possible!
```

### Inferential Tests

Relevant T-test and ANOVA will be conducted.

#### Conducting Independent Sample T-test price_diff vs house pricing ------------------
If the difference in prices is dependent on higher or lower house prices
**Null hypothesis - H0**
**Alternate hypothesis - H1**

H0 - There is no effect on difference in prices due to house pricing 
H1 - There is an effect on difference in prices due to house pricing
```{r}
t.test(diffdb$price_diff ~ diffdb$price_cat)
```

Since the p-value (0.0002812) < 0.05, then null-hypothesis is rejected.


#### Conducting Independent Sample T-test: price_diff vs no. of bedrooms ---------------
If the difference in prices is dependent on no. of bedrooms

H0 - There is no effect on difference in prices due to no. of  bedrooms 
H1 - There is an effect on difference in prices due to no. of  bedrooms

```{r}
t.test(diffdb$price_diff ~ diffdb$bed_cat)
```

Since the p-value (0.001919) < 0.05, then null-hypothesis is rejected.


#### Conducting Independent Sample T-test: price_diff vs no. of bathrooms  --------------
If the difference in prices is dependent on no. of bathrooms

H0 - There is no effect on difference in prices due to no. of bathrooms 
H1 - There is an effect on difference in prices due to no. of bathrooms
```{r}
t.test(diffdb$price_diff ~ diffdb$bath_cat)
```

Since the p-value (0.8833) > 0.05, then null-hypothesis is accepted.



#### Conducting One-way ANOVA test (more then 2 levels) --------------------------------
If the difference in prices is dependent on different areas in Dublin

H0 - There is no effect on difference in prices due to different areas in Dublin 
H1 - There is an effect on difference in prices due to different areas in Dublin
```{r}
anova_one_way <- aov(diffdb$price_diff ~ diffdb$dublin_code, data = diffdb)
summary(anova_one_way)
```

Since the p-value (0.0203) < 0.05, then null-hypothesis is rejected.


#### Conducting multiple regression with several levels in a categorical variable (dublin_code) ---------------------
```{r}
fit1 <- lm(price_diff ~ price + bed + bath + dublin_code, data = diffdb)
summary(fit1)
```

This implies the equation is like this - 

price_diff = 10874.90 + 0.00078(price) + 678.87(bedroom) - 561.17(bathroom) -11561.15(Dublin 11) - 10812.91(Dublin 13) - 10117.18(Dublin 15) - 12229.59(Dublin 17) - 11461.07(Dublin 3) - 11468.74(Dublin 5) - 12060.40(Dublin 7) - 10994.60(Dublin 9) - 12915.08(Co. Dublin)

If all the Dublin code values will be *equal to zero*, then for **Dublin 1**, 
price_diff = 10874.90 + 0.00078(price) + 678.87(bedroom) - 561.17(bathroom)

Further, by looking at the p-values, we can determine which variable will be statiscally significant for the variable price_diff.

```{r}
print("Thank you!")
```

