---
title: "Your Document Title"
author: "Document Author"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

## A New Output Format

`html_pretty` in the [**prettydoc**](https://github.com/yixuan/prettydoc/)
package is a new output format for creating HTML documents from R Markdown files.
`html_pretty` is more lightweight compared to `html_document`, and is more
stylish than `html_vignette` when creating package vignettes.

## New Styles

`html_pretty` currently supports three page themes (`cayman`, `tactile` and
`architect`), and two syntax highlight styles (`github` and `vignette`).
The theme and highlight styles can be specified in the document metadata,
for example:

```yaml
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
```

## Your Familiar Tools

```{r}
library(tidyverse)

library(modelr)
options(na.action = na.warn)

```

First model

```{r}
ggplot(sim1, aes(x, y)) + 
  geom_point()
```


```{r}
models <- tibble(
  a1 = runif(250, -20, 40),
  a2 = runif(250, -5, 5)
)



ggplot(sim1, aes(x, y)) + 
  geom_abline(aes(intercept = a1, slope = a2), data = models, alpha = 1/4) +
  geom_point() 
```


```{r}
model1 <- function(a, data) {
  a[1] + data$x * a[2]
}
model1(c(7, 1.5), sim1)




```

```{r}
measure_distance <- function(mod, data) {
  diff <- data$y - model1(mod, data)
  sqrt(mean(diff ^ 2))
}
measure_distance(c(7, 1.5), sim1)
```


```{r}
sim1_dist <- function(a1, a2) {
  measure_distance(c(a1, a2), sim1)
}

models <- models %>% 
  mutate(dist = purrr::map2_dbl(a1, a2, sim1_dist))



```

```{r}
ggplot(sim1, aes(x, y)) + 
  geom_point(size = 2, colour = "grey30") + 
  geom_abline(
    aes(intercept = a1, slope = a2, colour = -dist), 
    data = filter(models, rank(dist) <= 10)
  )
```



```{r}
grid <- expand.grid(
  a1 = seq(-5, 20, length = 25),
  a2 = seq(1, 3, length = 25)
  ) %>% 
  mutate(dist = purrr::map2_dbl(a1, a2, sim1_dist))


grid %>% 
  ggplot(aes(a1, a2)) +
  geom_point(data = filter(grid, rank(dist) <= 10), size = 4, colour = "red") +
  geom_point(aes(colour = -dist)) 

```





```{r}
ggplot(sim1, aes(x, y)) + 
  geom_point(size = 2, colour = "grey30") + 
  geom_abline(
    aes(intercept = a1, slope = a2, colour = -dist), 
    data = filter(grid, rank(dist) <= 10)
  )
```


```{r}
best <- optim(c(0, 0), measure_distance, data = sim1)
best$par
#> [1] 4.222248 2.051204

ggplot(sim1, aes(x, y)) + 
  geom_point(size = 2, colour = "grey30") + 
  geom_abline(intercept = best$par[1], slope = best$par[2])
```
```{r}
sim1_mod <- lm(y ~ x, data = sim1)
coef(sim1_mod)
```

